On the Construction of Isomorphic Interpreters (Journal Version)

### 2012-02-23 iso-int/iso-int.tex
_

\begin{document}
\title{Isomorphic Interpreters in {{langRevT}} (Journal Version)} 
\titlerunning{On the construction of Isomorphic Interpreters} 
\author{Roshan P. James \and Amr Sabry}
\institute{School of Informatics and Computing, Indiana University\\
\mails}
\maketitle

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simple Bounded Iterator}
Consider definition for the following small-step abstract machine:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Isomorphic Interpreters from Algebraic manipulation}

@@

>>>>

\begin{document}
\title{On the Construction of Isomorphic Interpreters (Journal Version)} 
\titlerunning{On the construction of Isomorphic Interpreters} 
\author{Roshan P. James \and Amr Sabry}
\institute{School of Informatics and Computing, Indiana University\\
\mails}
\maketitle

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Isomorphic Interpreters from Logically Reversible Abstract Machines}
\subsection{Simple Bounded Iterator}

Consider definition for the following small-step abstract machine:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Generating Inductive Walks for Algebraic Data Types}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Isomorphic Interpreters from Algebraic Manipulation}

@@

- Control theory

- Fiore's conditions

- b7 = b (two derivations)
